### 2023-03-20 main.tex
CheckFormula3.3.16
IntegrabilityFixed

    E=\sum_{a=2}^{N}E_{a2}

@@

\section{Integrability}\label{sec4}
We study the explicit steady state and the exact formulas for the correlations in the case of hard-core interaction ($\twoj=1$), i.e. when at most one particle of any is allowed in each site at any time. We simplify the geometry to a one dimensional chain $\{1,\ldots,L\}$ of length $L$ with boundaries at the ends. We assume a nearest neighbor interaction, i.e. we fix the conductances as follows

@@

    1\quad \text{if}\quad |x-y|=1\\

@@

$\forall x,y\in \{1,\ldots,L\}$.\\
The local inhomogeneities are chosen as follows: $\Gamma_{x}=0$ $\forall x\in \{2,\ldots,L-1\}$ and $\Gamma_{1}=\Gamma_{L}=1$. \\
We can think about the species $1$ as the empty state of the chain. This will be useful in the correlation formula.\\
In this section we will denote the element of the representation of the Lie algebra by lowercase letters, i.e. $e_{ab}$, since we are in the lowest spin case (the fundamental representation of algebra). \\

@@

	\Omega=\left\{|n\rangle=|n_{1},\ldots,n_{N}\rangle\;:\;n\in\mathbb{N}_0^N\;\;|n|=1\right\}^{L}

@@

	H=B_{1}+\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}+B_{L}

@@

@@

and boundary terms 

@@

where the rates satisfy

@@

{\color{red} I will add a figure with the boundary driven chain}\\
The steady state can be found by the \textit{matrix product ansatz}, that was introduced for the multispecies hard-core stirring in \cite{vanicat2017exact}. The formulation is the following. We aim to compute $|\Psi\rangle$ such that 

@@

The matrix product ansatz tells:

@@

@@

where $X_{a}$ for $s=1,\ldots,N$ are operators on an auxiliary space $V_{0}$ while $|V\rangle\in V_{0}$ and $\langle W|\in V_{0}^{*}$ (the dual space), such that $\langle W|V\rangle=1$. \\
They fulfill

@@

@@

\textbf{Remark}: Only $N-1$ of \eqref{leftBoundary} and \eqref{rightBoundary} are independent, indeed because of \eqref{ratesConditions} and \eqref{lambdaConditions}

@@

	gives $0=0$. Similar computations for the right boundary.\\
 The operators defined in \eqref{bulk},\eqref{leftBoundary},\eqref{rightBoundary} are not known explicitly. Via commutation relation is possible to compute some of the correlations. However, it would be interesting to write formulas for arbitrary correlations and the steady state, apart any choice of the form of the operators. \\
 We introduce some similarity transformations for the Hamiltonian \eqref{hamiltonian}. These allow to define two simpler Hamiltonians whose steady state can be  compute exactly. Reversing back the transformation we will obtain the original steady state. \\ 
We first use the \textit{dual similarity transformation}, defined by the symmetry operator \eqref{e_def}.
    V=\text{exp}\left(\sum_{a=2}^{N}e_{a1}\right)=e^{E}
Up to the diagonal matrix $R_{x}$, this is exactly the edge duality matrix. Then, we introduce the Hamiltonian
	H_{dual}=B_{1}^{dual}+\mathcal{H}+B_{L}^{dual}
It is linked to the original one by: 
\begin{equation}\label{uno}
	{H}^{T}V=V{H}_{dual}\quad \Rightarrow \quad {H}=\left(V^{-1}\right)^{T}{H}_{dual}^{T}V^{T}

We introduce the \textit{S similarity transformation} 
\begin{equation}\label{Esse}
    S=\exp \left(-\sum_{a=2}^N \beta_ae_{a1}\right)\exp \left(\sum_{b=2}^N e_{1b}\right)
and then the Hamiltonian 
\begin{equation}\label{diagHamiltonian}
    \widetilde{H}=\widetilde{B}_{1}+\mathcal{H}+\widetilde{B}_{L}
that is linked to the original one by 
\begin{equation}\label{due}
    HS=S\widetilde{H}\quad \Rightarrow \quad {H}=S\widetilde{H}S^{-1}
This \eqref{diagHamiltonian} has simpler boundary: the left one is lower triangular and the right one is diagonal. The bulk part remains the same. 
Indeed, by applying the similarity transformation \eqref{Esse} to the Hamiltonian we have:
	\widetilde{B}_{1}=SB_{1}S^{-1}=\begin{pmatrix}

@@

		\alpha_{N-1}-\beta_{N-1}&0&\vdots&-1&0\\
		\alpha_{N}-\beta_{N}&0&\vdots&0&-1

@@

	\widetilde{B}_{L}=SB_{L}S^{-1}=\begin{pmatrix}
		-1&0&\ldots&0&0\\

@@

		0&0&\vdots&-1&0\\
		0&0&\vdots&0&0
	\end{pmatrix}=e_{NN}-\id
	(S\otimes S)H_{x,x+1}(S\otimes S)^{-1}=H_{x,x+1}
that also implies that \eqref{Esse} is a symmetry of the bulk part of the Hamiltonian, since  
	(S\otimes S)H_{x,x+1}=H_{x,x+1}(S\otimes S)
The relation with the original Hamiltonian is found by imposing \eqref{uno}=\eqref{due}.
		\left(V^{-1}\right)^{T}H_{dual}^{T}V^{T}&=S\widetilde{H}S^{-1}\\
		VH_{dual}V^{-1}&=S^{T}\widetilde{H}^{T}\left(S^{-1}\right)^{T}\\
		H_{dual}&=V^{-1}S^{T}\widetilde{H}^{T}\left(S^{-1}\right)^{T}V\\
		H_{dual}&=T^{-1}\widetilde{H}^{T}T

@@

	T:=\left(S^{-1}\right)^{T}V
Associated to these new Hamiltonians we can define their steady states: 
	H|\Psi\rangle=0\qquad \widetilde{H}|\widetilde{\Psi}\rangle=0\qquad H_{dual}^{T}|\Psi_{ABS}\rangle=0
that are linked each others as follows
\begin{equation}\label{SteadyStates}
	|\Psi\rangle=\left(S^{-1}\right)^{\otimes L}|\widetilde{\Psi}\rangle\qquad |\Psi\rangle =\left((V^{T})^{-1}\right)^{\otimes L}|\Psi_{ABS}\rangle \qquad |\Psi_{ABS}\rangle=\left(T^{T}\right)^{\otimes L}|\widetilde{\Psi}\rangle
We can exploit \eqref{SteadyStates}, to compute the steady state of the original Hamiltonian \eqref{hamiltonian}.
\subsection{Absorption probabilities}
\subsubsection*{The steady state of $\widetilde{H}$}
We will show that the steady state $|\widetilde{\Psi}\rangle$ of $\widetilde{H}$ is the following 

@@

	|\widetilde{\Psi}\rangle=\sum_{s_{1},\ldots,s_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{i=1}^{L}\delta_{s_{i},1}\right)}{\Gamma\left(L+2\right)}\prod_{i=1}^{L}\left[\lambda_{s_{i}}\left(1+\sum_{j=i}^{L}\delta_{s_{j},1}\right)\right]^{1-\delta_{s_{i},1}}|\mathbf{s}\rangle

@@

and the basis vector $|s\rangle =\bigotimes_{i=1}^{L}|s_{i}\rangle$ with $s_{i}\in\{1,\ldots,N\}$ denotes the species that occupies the site $i\in \{1,\ldots,L\}$.
\\
By applying the $S$ to the vector $\left(X_{1},\ldots,X_{N}\right)$ 	we obtain new operators of the matrix product ansatz that can be written as: 

@@

we can also reverse the transformation by $S^{-1}$ and get: 

@@

These new $\widetilde{X}_{a}$ $\forall a\in \{1,\ldots,N\}$ satisfy new commutation relations.\\ 
Summing over \eqref{bulk} we get

@@

such that it immediately follows that

@@

We further get

@@

@@

	|V \rangle |\mathbf{n}\rangle

@@

such that for each site $x\in \{1,\ldots,L\}$ they must fulfill the hard-core constraint $$\sum_{a=1}^{N}n_{a}^{x}=1$$
The vector $|\widetilde{\Psi}\rangle $ has dimension $N^{L}$. \\
We need to compute the coefficient $\langle W|\prod_{i=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{m_{a}^{i}}

@@

We can rewrite \eqref{commutationsBulk} as:

@@

We first observe that $\forall a\in \{2,\ldots,N\}$ and $\forall l,n\in \mathbb{N}$ we have, thanks to \eqref{UsefulRelation}: 
	\widetilde{X}_{a}^{n}\widetilde{X}_{1}^{l}&=\widetilde{X}_{a}^{n-1}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{l-1}
	\\&=\lambda_{a}\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}^{l}+\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}\widetilde{X}_{a}\widetilde{X}_{1}^{l-1}

@@

	\lambda_{a}\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{l-1}+\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{l-1}

@@

	\widetilde{X}_{1}^{l}\left(\widetilde{X}_{a}+l\lambda_{a}\right)^{n}

@@

by consequence

@@

Thus we obtain

@@

by using \eqref{commRIGHT}

@@

we only need to compute $\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}|V\rangle$. For the sake of notation call $\sum_{i=1}^{L}n_{1}^{i}=n_{1}$. Take an arbitrary $a\in \{2,\ldots,N\}$
	\langle W|\widetilde{X}_{1}^{m_{1}}|V\rangle&=\langle W|\widetilde{X}_{1}\widetilde{X}_{1}^{n_{1}-1}|V\rangle=\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle +\langle W|\frac{1}{\lambda_{a}}\widetilde{X}_{a}\widetilde{X}_{1}^{n_{1}-1}|V\rangle

@@

we have a recursion

@@

@@

we add the normalization

@@

All in all

@@

 We now perform a change of basis. By calling $s_{i}$ the (only) species present at site $i$, we can rewrite

@@

where $s_i=\sum_{k=1}^Nk\delta_{n_k^i,1}$. 
Then it is to see that 

@@

with $s_{i}\in\{1,\ldots,N\}$.     
\\Moreover, for a fixed site $i$, the coefficient
	\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{i}}\left(1+\sum_{j=i}^{L}n_{1}^{j}\right)^{n_{a}^{i}}
has only one factor, associated to the non empty species $a$ that is the site $i$, i.e. to the only $m_{a}^{i}\neq 0$. Furthermore, if the site $i$ has the empty, i.e. $1$, the whole coefficient equals 1. The $m_{1}^{i}$ are one if and only if the occupation of site $i$ is $1$, then it easy to see that $m_{1}^{i}=\delta_{s_{i},1}$. Then, we can write

@@

As already pointed out, $m_{1}^{i}=\delta_{s_{i},1}$, then 

@@

Finally, making the sum over all $\mathbf{s}\in \Omega$ is equivalent to sum over all the possible values of each $s_{i}\in\{1,\ldots,N\}$ $\forall i\in\{1,\ldots,L\}$. Thus, by putting all these things together, we obtain \eqref{ResulsBasis} from \eqref{resulEsteady}
\subsubsection*{The steady state of $H_{dual}^{T}$}
The steady state $|\Psi_{ABS}\rangle$ such that $H_{dual}^{T}|\Psi_{abs}\rangle=0$ is given by the following formula:

@@

			|\Psi_{ABS}\rangle=\sum_{s_{1},\ldots,s_{L}=1}^{N}\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(1+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}\bigotimes_{r=1}^{L} |s_{r}\rangle
 By \eqref{SteadyStates}, we first need to compute $(T^{T})^{\otimes L}$. 
The matrix $T$ has the following form
\begin{equation}\label{ExplicitMatrixT}
	T=\exp\left(-\sum_{b=2}^{N}e_{b1}\right)\exp\left(\sum_{a=2}^{N}\beta_{a}e_{1a}\right)\exp\left(\sum_{b=2}^{N}e_{b1}\right)=\exp\left(\sum_{a=2}^{N}\beta_{a}e_{1a}\right)
	T=I_{N\times N}+\begin{pmatrix}
		0&\beta_{2}&\ldots&\beta_{N}\\
		\vdots&\vdots&\ldots&\vdots\\
		0&0&\ldots&0
We introduce the following notation: $e_{a}^{b}=e_{ab}$, $e_{ab}\otimes e_{cd}=e_{a,c}^{b,d}$ and $$\delta_{a,b}=\begin{cases}
	1\quad \text{if}\quad a=b\\
	0\quad \text{if}\quad a\neq b
\end{cases}$$ 
Then we have that 
	T^{T}=I_{N\times N}+\begin{pmatrix}
		\beta_{2}&0&\ldots&0\\
		\vdots&\vdots&\ldots&\vdots\\
		\beta_{N}&0&\ldots&0
	\end{pmatrix}=\sum_{s_{1}=1}^{N}e_{i}^{i}+(1-\delta_{s_{1},1})\sum_{s_{1}=2}^{N}\beta_{s_{1}}e_{s_{1}}^{1}
For the sake of notation let us introduce also the following matrix
We start by computing 
	T^{T}\otimes T^{T}=\left(I_{N\times N}+Q\right)\otimes\left(I_{N\times N}+Q\right)=I_{N\times N}\otimes I_{N\times N}+I_{N\times N}\otimes Q+Q\otimes I_{N\times N}+Q\otimes Q
Let's compute each terms separately:
	I_{N\times N}\otimes I_{N\times N}=\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}\otimes \sum_{s_{2}=1}^{N}e_{s_{2}}^{s_{2}}=\sum_{s_{1},s_{2}=1}^{N}e_{s_{1},s_{2}}^{s_{1},s_{2}}
	I_{N\times N}\otimes Q=(1-\delta_{s_{2},1})\sum_{s_{1}=1}^{N}e_{s_{1}}^{s_{1}}\otimes \sum_{s_{2}=2}^{N}\beta_{s_{2}}e_{s_{2}}^{1}=(1-\delta_{s_{2},1})\sum_{s_{1}=1,s_{2}=2}^{N}e_{s_{1},s_{2}}^{s_{1},1}\beta_{s_{2}}
	Q\otimes I_{N\times N}=(1-\delta_{s_{1},1})\sum_{s_{1}=2}^{N}\beta_{s_{1}}e_{s_{1}}^{1}\otimes \sum_{s_{2}=1}^{N}e_{s_{2}}^{s_{2}}=(1-\delta_{s_{1},1})\sum_{s_{1}=2,s_{2}=1}^{N}e_{s_{1},s_{2}}^{1,s_{2}}\beta_{s_{1}}
	Q\otimes Q=(1-\delta_{s_{1},1})(1-\delta_{s_{2},1})\sum_{s_{1}=2}^{N}\beta_{s_{1}}e_{s_{1}}^{1}\otimes \sum_{s_{2}=2}^{N}\beta_{s_{2}}e_{s_{2}}^{1}=(1-\delta_{s_{1},1})(1-\delta_{s_{2},1})\sum_{s_{1},s_{2}=2}^{N}\delta_{s_{1},s_{2}}^{1,1}\beta_{s_{1}}\beta_{s_{2}}
Take a line of the matrix $T^{T}\otimes T^{T}$ identified by index $(s_{1},s_{2})$, then it can be written as
	\left(T^{T}\otimes T^{T}\right)_{(s_{1},s_{2})}=e_{s_{1},s_{2}}^{s_{1},s_{2}}+(1-\delta_{s_{2},1})\beta_{s_{2}}e_{s_{1},s_{2}}^{s_{1},1}+(1-\delta_{s_{1},1})\beta_{s_{1}}e_{s_{1},s_{2}}^{1,s_{2}}+(1-\delta_{s_{1},1})(1-e_{s_{2},1})\beta_{s_{1}}\beta_{s_{2}}e_{s_{1},s_{2}}^{1,1}
Then it is easy to generalize for an arbitrary order of tensor product. Take the configuration with $L$ sites and identify the row $\mathbf{s}=(s_{1},\ldots,s_{L})$ with $s_{i}\in \{1,\ldots,N\}$, $\forall i\in\{1,\ldots,L\}$:
		\left(T^{T}\right)^{\otimes L}_{s_{1},\ldots,s_{L}}&=e_{s_{1},\ldots,s_{L}}^{s_{1},\ldots,s_{L}}+\sum_{k_{1}=s_{1},\ldots,s_{L}\,:\,k_{1}\neq 1}e_{s_{1},\ldots,k_{1},\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,s_{L}}\beta_{k_{1}}\\&+\sum_{k_{1},k_{2}=s_{1},\ldots,s_{L}\,:\,k_{1},k_{2}\neq 1}e_{s_{1},\ldots,k_{1},\ldots,k_{2}\ldots,s_{L}}^{s_{1},\ldots,1,\ldots,1,\ldots,s_{L}}\beta_{k_{1}}\beta_{k_{2}}+\ldots+\left(\sum_{i=1}^{L}(1-\delta_{s_{i},1})\right)\prod_{i=1}^{L}\left(\beta_{s_{i}}\right)^{1-\delta_{s_{i},1}}e_{s_{1},\ldots,s_{L}}^{1,\ldots,1}
Then, by multiplying this matrix for the vector $|\widetilde{\Psi}\rangle$ we obtain

>>>>

    E=\sum_{a=2}^{N}E_{a1}

@@

\section{Integrability}\label{sectionIntegrabiliy}
\subsection{The integrable chain and the matrix product ansatz}
In this section we specialize the multi-species stirring process to the geometry of the one dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs are connected with the end site $1$ and $L$. These boundaries, exchanges particle with the external environment, putting the chain out of equilibrium. To use integrability is better to work with Hamiltonians. The Hamiltonian that we consider here is obtained by \eqref{OriginalHamiltonian} assuming that the conducatances are

@@

    1 \quad \text{if}\quad |x-y|=1\\

@@

and the local inhomogeneities are
    \Gamma_{x}=\begin{cases}
        1\quad \text{if} \quad x\in \{1,L\}\\
We further assume that the maximal occupancy in each site is $\nu=1$, i.e. that there is an \textit{hard-core interaction}.
We will denote the element of the representation of the Lie algebra by lowercase letters, i.e. $e_{ab}$, since we are in the lowest spin case (the fundamental representation of algebra). \\

@@

    \Omega=\bigtimes_{x=1}^{L}\Omega_{x}
	\Omega_{x}=\left\{|n\rangle=|n_{1},\ldots,n_{N}\rangle\;:\;n\in\mathbb{N}_0^N\;\;|n|=1\right\}

@@

	H=B_{1}+H_{bulk}+B_{L}

@@

    H_{bulk}=\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}
Moreover, for a fixed site $x\in \{1,\ldots,L\}$ we have 

@@

The boundary terms are given by 

@@

where we assume that the parameters satisfy

@@

Under these assumption the Hamiltonian \eqref{hamiltonian} is integrable and a matrix product anstz (MPA) for the non-equilibrium steady state is available (see\cite{vanicat}). We recall the main points of this ansatz. \\
 Calling $|\mathbb{P}(t)\rangle$ a vector that contains the probability of every configuration of the chain with Hamiltonian \eqref{hamiltonian} at time $t\geq 0$, its evolution equation is given by 
    \frac{d|\mathbb{P}(t)}{dt}=H|\mathbb{P}(t)\rangle
We define the steady state of $H$ defined in \eqref{hamiltonian} a vector, denoted by $|\Psi\rangle$ that contains the probabilities of every configuration of the chain with respect to the stationary distribution, i.e. the probability distribution that the chain reaches when $t\to \infty$. We observe that, since the Markov chain with Hamiltonian \eqref{hamiltonian} is positive recurrent there exists a unique stationary distribution and, moreover, this is distribution is reached when $t\to \infty$ starting for every arbitrary initial distribution. 
 Therefore, to find the stationary state, we aim to compute $|\Psi\rangle$ such that 

@@

The MPA states the following

@@

with the normalization 

@@

where $X_{a}$ for $a=1,\ldots,N$ are operators on an auxiliary space $V_{0}$ while $|V\rangle\in V_{0}$ and $\langle W|\in V_{0}^{*}$ ( where $V^{*}$ denotes the algebraic dual space), such that $\langle W|V\rangle=1$. $\langle W|$ and $|V\rangle$ are sometimes called boundary vectors. These operators $(X_{a})_{a\in \{1,\ldots,N\}}$ fulfil the commutators

@@

and their action on the boundary vectors are

@@

\textbf{Remark}: only $N-1$ of \eqref{leftBoundary} and \eqref{rightBoundary} are independent, indeed because of \eqref{ratesConditions} and \eqref{lambdaConditions}

@@

	gives $0=0$. Similar computations can be done for the right boundary.
\subsection{The exact steady state for the multi-species stirring process on a chain}\label{subsection-exact}
We aim to find an explicit for for the steady state $|\Psi\rangle$. The MPA states the form of the steady state in function of an abstract algebra of operators. If an explicit representation of $(X_{a})_{a=1,\ldots,N}$ was available, it would be possible to compute explicitly all the correlations and currents of particles for the Hamiltonian \eqref{hamiltonian}. Another way of computing this steady state, without passing through a representation, is using the commutators \eqref{bulk} and the actions \eqref{leftBoundary} and \eqref{rightBoundary}. For the one and two point correlation and for the currents this has been done in \cite{vanicat}. Inspired by this last reference, in this subsection, we aim to find exact formulas for the steady state of \eqref{hamiltonian} using only the \eqref{bulk}, \eqref{leftBoundary} and \eqref{rightBoundary}. In subsection \eqref{correlation-section}, this result will leads to exact correlation for arbitrary number of particles of type $\{2,\ldots,N\}$. This aim will be achieved by the help of a similarity transformation $\mathcal{S}$ that makes commutation relation simpler, and allows to find the steady state of a transformed Hamiltonian, that will be denoted by $\mathbb{H}$, with lower-triangular left boundary and diagonal right boundary. Therefore, inverting this similarity, one can retrieve the steady state of \eqref{hamiltonian}. A fundamental 'ingredient' of these computation is duality, that has been proved in section \ref{sectionDuality}. 
\subsubsection{The similarity transformation}
We aim to construct a similarity transformation that maps the Hamiltonian \eqref{hamiltonian} into an other $\mathbb{H}$ that has left boundary lower-triangular and right boundary diagonal. Consider the transformation
\begin{equation}\label{transformationV}
 V:=\exp{\left(\sum_{a=2}^{N}e_{a1}\right)}=\mathbbm{1}+\sum_{a=2}^{N}e_{a1}
Observe that it is the the duality matrix at site $x\in \{1,\ldots,L\}$ up to the multiplication by $R_{x}$. By taking the tensor product over the chain we define
    \mathcal{V}=V^{\otimes L}
 This matrix $\mathcal{V}$ is invertible and we introduce 
\begin{equation}\label{hatHamiltonian}
    \widehat{H}:=\widehat{B}_{1}+\mathcal{H}+\widehat{B}_{L}
\begin{equation}\label{similarV}
   H=\left(\mathcal{V}^{-1}\right)^{T}\widehat{H}^{T}V^{T}
Using \eqref{transformationV} we introduce the \textit{similarity transformation} 
\begin{equation}\label{similarity}
    S:=\sum_{a=2}^{N}\beta_{a}\sum_{b=2}^{N}e_{ab}+V=-\sum_{a=2}^{N}\beta_{a}\sum_{b=2}^{N}e_{ab}+\exp{\left(\sum_{a=2}^{N}e_{1a}\right)}
Taking the tensor product over the sites of the chain we further define
    \mathcal{S}:=S^{\otimes L}
Therefore, we call
\begin{equation}\label{bbHamiltonian}
    \mathbb{H}=\mathbb{B}_{1}+H_{bulk}+\mathbb{B}_{L}
\begin{equation}\label{similarS}
    H=\mathcal{S}^{-1} \mathbb{H}\mathcal{S}
The Hamiltonian $\mathbb{H}$ has lower-triangular left boundary and diagonal right boundary, i.e.
    \mathbb{B}_{1}=SB_{1}S^{-1}=e_{11}-\mathbbm{1}+\sum_{a=2}^{N}\left(\alpha_{a}-\beta_{a}\right)e_{a1}=\begin{pmatrix}

@@

		\alpha_{N-1}-\beta_{N-1}&0&\ldots&-1&0\\
		\alpha_{N}-\beta_{N}&0&\ldots&0&-1

@@

    \mathbb{B}_{L}=SB_{L}S^{-1}=e_{11}-\mathbbm{1}=\begin{pmatrix}

@@

		0&0&\ldots&-1&0\\
		0&0&\ldots&0&-1
The bulk part of $\mathbb{H}$ is left unchanged by this transformation, i.e.
    \mathcal{H}_{x,x+1}=\left(S\otimes S\right)\mathcal{H}_{x,x+1}\left(S\otimes S\right)^{-1}
In the following of our analysis it will be useful to have a relation between \eqref{hatHamiltonian} and \eqref{bbHamiltonian}. This relation reads as
    \widehat{H}=\mathcal{T}^{-1}\mathbb{H}\;\mathcal{T}

@@

    T=\left(S^{-1}\right)^{T}V=\exp{\left(\sum_{a=2}^{N}\beta_{a}e_{1a}\right)}
    \mathcal{T}:=T^{\otimes L}
Indeed, by imposing equal \eqref{similarV} and \eqref{similarS} we obtain 
    		\left(\mathcal{V}^{-1}\right)^{T}\widehat{H}^{T}\mathcal{V}^{T}&=\mathcal{S}\mathbb{H}\mathcal{S}^{-1}\\
		\mathcal{V}\widehat{H}\mathcal{V}^{-1}&=\mathcal{S}^{T}\mathbb{H}^{T}\left(\mathcal{S}^{-1}\right)^{T}\\
		\widehat{H}&=\mathcal{V}^{-1}\mathcal{S}^{T}\mathbb{H}^{T}\left(\mathcal{S}^{-1}\right)^{T}\mathcal{V}\\
		\widehat{H}&=\mathcal{T}^{-1}\mathbb{H}^{T}\mathcal{T}
Associated with these new Hamiltonians $\widehat{H}$ and $\mathbb{H}$ we define the following steady states
	\mathbb{H}|\widetilde{\Psi}\rangle=0\qquad \widehat{H}^{T}|\widehat{\Psi}\rangle=0
The steady states $|\Psi\rangle$, $|\widehat{\Psi}\rangle$ and $|\widetilde{\Psi}\rangle$ are linked by 
	|\Psi\rangle=&\left(\mathcal{S}^{-1}\right)|\widetilde{\Psi}\rangle\label{SteadystateTilde}
 \\|\Psi\rangle =&\left((\mathcal{{V}}^{T})^{-1}\right)|\widehat{\Psi}\rangle \label{SteadystateHat}
 \\|\widehat{\Psi}\rangle=&\left(\mathcal{T}^{T}\right)|\widetilde{\Psi}\rangle\label{SteadyStateHatTilde}
In the following subsections we will first compute the steady state $|\widetilde{\Psi}\rangle$. Then, using the transformation $\mathcal{T}$ we will retrieve $|\widehat{\Psi}\rangle$. Finally, using the transformation $\mathcal{V}$ we will find $|\Psi\rangle$. 
\subsubsection{The steady state of $\mathbb{H}$}
We state the following result. The steady state of the Hamiltonian $\mathbb{H}$ defined in \eqref{bbHamiltonian} is given by 

@@

	|\widetilde{\Psi}\rangle=\sum_{s_{1},\ldots,s_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{i=1}^{L}\delta_{s_{i},1}\right)}{\Gamma\left(L+2\right)}\prod_{i=1}^{L}\left[\lambda_{s_{i}}\left(1+\sum_{j=i}^{L}\delta_{s_{j},1}\right)\right]^{1-\delta_{s_{i},1}}|\mathbf{\bm{s}}\rangle

@@

and the basis vector $|\bm{s}\rangle =\bigotimes_{i=1}^{L}|s_{i}\rangle$ with $s_{i}\in\{1,\ldots,N\}$ denotes the species that occupies the site $i\in \{1,\ldots,L\}$.
\paragraph{Proof of formula \eqref{ResulsBasis}} 
To prove \eqref{ResulsBasis} we will consider the vector composed by the operators of the MPA $(X_{1},\ldots,X_{N})$ and we will act on it with the similarity transformation \eqref{similarity} obtaining new operators $(\Xt_{1},\ldots,\Xt_{N})$ that will satisfy simpler commutators than \eqref{bulk} and simpler actions than \eqref{leftBoundary} and \eqref{rightBoundary}. This will allow to write explicitly the steady state \eqref{ResulsBasis}.
For the sake of notation, we denote by 
	\end{pmatrix}\quad \forall a\in \{2,\ldots,N\}
We obtain the new operators of the MPA that by transforming the original one by \eqref{similarity} 

@@

We can also reverse the transformation by $S^{-1}$ and get back: 

@@

Summing over $b\in \{1,\ldots,N\}$ in \eqref{bulk} we have

@@

therefore, we obtain the commutation relations for $\Xt_{a}$ $\forall a\in \{1,\ldots,N\}$

@@

Moreover using \eqref{Xtildes2b} and \eqref{Xes}, the action of $\Xt_{a}$ $\forall a\in \{1,\ldots,N\}$ on the boundary vectors are given by 

@@

\begin{equation}\label{toDetermineTilde}

@@

	|V \rangle \,|\mathbf{n}\rangle

@@

such that for each site $x\in \{1,\ldots,L\}$ $|n^{x}\rangle=|n_{1}^{x},\ldots,n_{N}^{x}\rangle\in \Omega_{x}$. 
We also observe that the vector $|\widetilde{\Psi}\rangle $ has dimension $N^{L}$. \\
To determine the steady state \eqref{toDetermineTilde}, we need to compute the coefficient $\langle W|\prod_{i=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{m_{a}^{i}}

@@

We  rewrite \eqref{commutationsBulk} as:

@@

Fixing $ a\in \{2,\ldots,N\}$ and $\forall \ell,n\in \mathbb{N}$ and applying many times \eqref{UsefulRelation} we have
	\widetilde{X}_{a}^{n}\widetilde{X}_{1}^{\ell}&=\widetilde{X}_{a}^{n-1}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{N}^{\ell-1}
	\\&=\lambda_{a}\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}^{\ell}+\widetilde{X}_{a}^{n-1}\widetilde{X}_{1}\widetilde{X}_{a}\widetilde{X}_{1}^{\ell-1}

@@

	\lambda_{a}\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{\ell-1}+\widetilde{X}_{a}^{n-2}\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\left(\lambda_{a}\widetilde{X}_{1}+\widetilde{X}_{1}\widetilde{X}_{a}\right)\widetilde{X}_{1}^{\ell-1}

@@

	\widetilde{X}_{1}^{\ell}\left(\widetilde{X}_{a}+\ell\lambda_{a}\right)^{n}
therefore 

@@

By taking the product over the sites $i$ from $1$ to L we obtain 

@@

Therefore, multiplying by the boundary vectors we have 

@@

Using \eqref{commRIGHT}

@@

To determine the state we need to compute $\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}|V\rangle$. Calling $\sum_{i=1}^{L}n_{1}^{i}=n_{1}$ and taking an arbitrary $a\in \{2,\ldots,N\}$ we have
	\langle W|\widetilde{X}_{1}^{n_{1}}|V\rangle&=\langle W|\widetilde{X}_{1}\widetilde{X}_{1}^{n_{1}-1}|V\rangle=\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle +\langle W|\frac{1}{\lambda_{a}}\widetilde{X}_{a}\widetilde{X}_{1}^{n_{1}-1}|V\rangle

@@

This leads to the recursion relation

@@

that implies 

@@

The normalization constant is computed similarly as 

@@

Therefore, we write the coefficients of the linear combination \eqref{toDetermineTilde} as 

@@

Calling $s_{i}$ the species present at site $i$, we rewrite the basis vector 

@@

where $s_i=\sum_{k=1}^N\delta_{n_k^i,1}$. Finally we take the tensor product of the vectors $|s_{i}\rangle$ and we obtain

@@

with $s_{i}\in\{1,\ldots,N\}$. For a fixed site $i$, because of the hard-core interaction that allows at most one particle on type different from $1$ ,at site $i$ we have 

@@

Moreover, we have 

@@

Finally summing over all $\mathbf{s}\in \Omega$ (that is equivalent, $\forall i\in\{1,\ldots,L\}$, to summing over all the possible values of each $s_{i}\in\{1,\ldots,N\}$) we obtain \eqref{ResulsBasis} from \eqref{resulEsteady}.
\subsubsection{The steady state of $\widehat{H}$}
Knowing the steady state \eqref{ResulsBasis} of the Hamiltonian $\mathbb{H}$ defined in \eqref{bbHamiltonian}, we use \eqref{SteadyStateHatTilde} to retrieve the steady state of the Hamiltonian $\widehat{H}$ defined in \eqref{hatHamiltonian}. The result is the following 
\begin{equation}\label{ABS-vect}
    |\widehat{\Psi}\rangle =\sum_{s_{1},\ldots,s_{L}=1}^{N}\widehat{\Psi}(\bm{s})|\bm{s}\rangle 

@@

			\widehat{\Psi}(\bm{s})=\sum_{i=1}^{L}\sum_{c_{i}=0}^{1-\delta_{s_{i},1}}\frac{\Gamma(2+L-\sum_{k=1}^{L}c_{k})}{\Gamma(L+2)}\prod_{l=1}^{L}\left(\lambda_{s_{l}}\left(1+L-l-\sum_{j=l}^{L}c_{j}\right)\right)^{c_{l}}\beta_{s_{l}}^{(1-c_{l})(1-\delta_{s_{l},1})}
 \begin{equation}\label{CiEquation}
